Untitled CAV Paper

### 2016-01-20 paper.tex
Added treeFormula algorithms and some explanation

\documentclass{llncs}

@@

>>>>

\documentclass{llncs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\pagestyle{headings}

@@

\subsection{Solving Bounded Runs}

An abstract game tree can be checked for a winning run by a SAT solver.  The
tree must be encoded into CNF by making copies of the transition relation for
each game step in tree. The formula must also check whether the error state has
been reached in no branch/in all branches for the controller and environment
respectively. The functions that produce these formulas are shown in Algorithm
\ref{alg:treeFormula}.

\begin{algorithm}
    \caption{Tree formulas for Controller and Environment respectively}
    \label{alg:treeFormula}
    \begin{algorithmic}
        \Function{treeFormula}{gt}
        \If{$\Call{rank}{gt} == 0$}
        \State \Return{ $\lnot \Call{E}{x^{gt}}$ }
        \Else
        \State \Return{ $\lnot \Call{E}{x^{gt}} \land \bigwedge_{n \in \Call{succ}{gt}}(\Call{$\delta$}{n} \land \Call{label}{n} \land \Call{treeFormula}{n})$ }
        \EndIf
        \EndFunction
    \end{algorithmic}

    \begin{algorithmic}
        \Function{$\overline{treeFormula}$}{gt}
        \If{$\Call{rank}{gt} == 0$}
        \State \Return{\Call{E}{$x^{gt}$}}
        \Else
        \State \Return{ $\Call{E}{x^{gt}} \lor \bigvee_{n \in \Call{succ}{gt}}(\Call{$\delta$}{n} \land \Call{label}{n} \land \Call{$\overline{treeFormula}$}{n})$ }
        \EndIf
        \EndFunction
    \end{algorithmic}
\end{algorithm}

When we produce a formula using $\textsc{treeFormula}$ the SAT solver is
playing on behalf on the controller. Any unfixed labels, controllable or
uncontrollable, in the tree will be existentially quantified. This means that
if there exists a way for the game to be solved when both players cooperate the
SAT solver will find it.

\subsection{Counterexample Guided Bounded Synthesis}
